Legends for supplementary material

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends
eddited legend for correlation figure

**Supplementary Table 1. Genomic Annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models. The GRCh37/hg19 human genome assembly was used. "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Available Cell Type" - the name of the cell type in which the annotation was available, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions). [??? Did you use only features common to both cell lines?; !!!clarified, need to discuss further]

@@

>>>>

**Supplementary Table 1. Genomic Annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models. The GRCh37/hg19 human genome assembly was used. "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Available Cell Type" - the name of the cell type in which the annotation was available, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).

@@

**Supplementary Figure 2. Correlations between genomic annotations across cell lines and resolutions.** Upper and lower correlation heatmaps between genomic annotations for the GM12878 (A-D) and K562 (E-H) cell lines, across the 10 kb, 25 kb, 50 kb, and 100 kb resolutions (A, B, C, D; and E, F, G, H respectively). The correlations were evaluated on the total number of overlapped bases between flanked TAD boundaries and genomic annotations. High correlations (red) denote annotations that tended to occur colocally near TAD boundaries. Low correlations (blue) denote annotations that did not tend to occur near TAD boundaries together.
